My title\thanks{Code and data are available at: https://github.com/Jingying-yu/Shanghai\_population\_change}

### 2024-12-02 paper/paper.tex
finished most of the data section, model section, and added to discussion section

\usepackage{float}
\usepackage{tabularray}
\usepackage[normalem]{ulem}
\usepackage{graphicx}
\UseTblrLibrary{booktabs}
\UseTblrLibrary{siunitx}
\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}
\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={My title},
  pdfauthor={Sandy Yu},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{My title\thanks{Code and data are available at:
https://github.com/Jingying-yu/Shanghai\_population\_change}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Impact Analysis of Japanese Occupation on Population Shifts
Across Shanghai's Districts During WWII}
\author{Sandy Yu}
\date{November 30, 2024}

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, breakable, frame hidden, boxrule=0pt, interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners]}{\end{tcolorbox}}\fi

@@

\begin{itemize}
\tightlist
\item
  talk about where the data in my primary reference book is gathered
\item
  mentions the credibility of source and unstability of recording
  instrument \& methodology
\end{itemize}

@@

Important Event Timeline 1. 1937-08-13: Japanese armed forces entered
Shanghai 2. 1937-11-12: Japanese armed forces claims occupation of
Shanghai --\textgreater{} ends Chinese district 3. 1942-01: Japanese
armed forces claims authority over International Settlement (which was
mainly under the governance of U.K and U.S prior to this date) 4.
1945-08-15: Japan surrendered in WWII 5. 1945-10: most Japanese armed
forces withdrawed from Shanghai

\hypertarget{measurement}{%
\subsection{Measurement}\label{measurement}}

\begin{itemize}
\tightlist
\item
  how population is recorded (not accurate count but by householad then
  estimates by average)
\item
  why use population density instead of pure population \#
\item
  how year variables correspond to the timeline (ex. if an event occured
  in Nov of 1937, would I take valeus of 1937 as a variable for prior to
  event occurance or after?)
\end{itemize}

\hypertarget{outcome-variables}{%
\subsection{Outcome variables}\label{outcome-variables}}

\begin{itemize}
\tightlist
\item
  outcome variable is ``population change in International Settlement
  during 1937-1942'' measured in population density
\end{itemize}

\hypertarget{predictor-variables}{%
\subsection{Predictor variables}\label{predictor-variables}}

\begin{itemize}
\tightlist
\item
  most important predictors include time sensitive indicators: Event1 \&
  Event2
\end{itemize}

Event1: indicator variable for 1937 (1 if year \textgreater= 1937 \&
\textless= 1941, 0 otherwise) - mention a bit about the measurement

Event2: indicator variable for 1937 (1 if year \textgreater= 1941, 0
otherwise) - mention a bit about the measurement

@@

Background details and diagnostics are included in
Appendix~\ref{sec-model-details}.

@@

\[y_{it}|\mu_{it}, \sigma \sim \mbox{Normal}(\mu_{it}, \sigma)\]

\[\mu_{it} = \alpha + \beta_1 \cdot \mbox{cd_occupied}_{it} + \beta_2 \cdot \mbox{french_surrender}_{it} + \beta_3 \cdot \mbox{is_occupied}_{it} + \beta_4 \cdot \mbox{district_type}_{i, IS} +
\\
\beta_5 \cdot \mbox{district_type}_{i, FC} + \beta_6 \cdot \mbox{cd_occupied}_{it} \cdot \mbox{district_type}_{i, IS} + 
\\
\beta_7 \cdot \mbox{cd_occupied}_{it} \cdot \mbox{district_type}_{i, FC} + \beta_8 \cdot \mbox{french_surrender}_{it} \cdot \mbox{district_type}_{i, IS} + 
\\
\beta_9 \cdot \mbox{french_surrender}_{it} \cdot \mbox{district_type}_{i, FC} + 
\\
\beta_{10} \cdot \mbox{is_occupied}_{it} \cdot \mbox{district_type}_{i, IS} + \beta_{11} \cdot \mbox{is_occupied}_{it} \cdot \mbox{district_type}_{i, FC}\]

\[\alpha \sim \mbox{Normal}(0, 2.5)\]

\[\beta_k \sim \mbox{Normal}(0, 2.5) \quad \mbox{for } k = 1, ..., 11\]

\[\sigma \sim \mbox{Exponential}(1)\]

\textbf{Where}:

\begin{itemize}
\tightlist
\item
  \(y_{i,t}\): Observed population in district i at year t.
\item
  \(\mbox{cd_occupied}_{i,t}\): Indicator for whether the
  Chinese-administered district was occupied by Japanese forces in year
  t (1 if \(t \geq 1937\), 0 otherwise).
\item
  \(\mbox{french_surrender}_{i,t}\): Indicator for the French
  Surrendering to Germany in 1940, leading to the French Concession
  rejecting refugees in Shanghai (1 if \(t \geq 1940\), 0 otherwise).
\item
  \(\mbox{is_occupied}_{i,t}\): Indicator for the Japanese occupation of
  the International Settlement in 1942 (1 if \(t \geq 1942\), 0
  otherwise).
\item
  \(\mbox{district_type}_{i, IS}\): Dummy variable for International
  Settlement districts (1 if i is IS, 0 otherwise).
\item
  \(\mbox{district_type}_{i, FC}\): Dummy variable for French Concession
  districts (1 if i is FC, 0 otherwise).
\end{itemize}

\textbf{Interaction Terms}: The interaction terms in the model are
essential because they capture how the impact of historical events
(e.g., the 1937 occupation of Chinese-administered districts, the 1940
refugee rejection in the French Concession, and the 1942 occupation of
the International Settlement) varies across different district types. By
including interactions between event indicators and district types, the
model accounts for district-specific responses to each event,
controlling for the fact that the effect of an event on population
changes may not be uniform across all districts. For instance, the 1937
occupation might lead to population declines in Chinese-administered
districts but population increases in the International Settlement due
to refugee influx. These terms ensure that the model can differentiate
and estimate the unique effects of each event within each district type,
thereby improving precision and interpretability.

\begin{itemize}
\tightlist
\item
  \(\mbox{cd_occupied}_{i,t} \cdot \mbox{district_type}_{i, IS}\):
  Captures the effect of the 1937 occupation on the International
  Settlement in comparison to the Chinese-administered district (base
  district).
\item
  \(\mbox{cd_occupied}_{i,t} \cdot \mbox{district_type}_{i, FC}\):
  Captures the effect of the 1937 occupation on the French Concession in
  comparison to the base district.
\item
  \(\mbox{french_surrender}_{i,t} \cdot \mbox{district_type}_{i, IS}\):
  Effect of the 1940 refugee rejection on the International Settlement.
\item
  \(\mbox{french_surrender}_{i,t} \cdot \mbox{district_type}_{i, FC}\):
  Effect of the 1940 refugee rejection on the French Concession.
\item
  \(\mbox{is_occupied}_{i,t} \cdot \mbox{district_type}_{i, IS}\):
  Effect of the 1942 occupation on the International Settlement.
\item
  \(\mbox{is_occupied}_{i,t} \cdot \mbox{district_type}_{i, FC}\):
  Effect of the 1942 occupation on the French Concession.
\end{itemize}

@@

Our results are summarized in Table~\ref{tbl-modelresults}.

\centering
\begin{tblr}[         %% tabularray outer open
]                     %% tabularray outer close
{                     %% tabularray inner open
colspec={Q[]Q[]},
column{1}={halign=l,},
column{2}={halign=c,},
hline{26}={1,2}{solid, 0.05em, black},
}                     %% tabularray inner close
\toprule
& Population model \\ \midrule %% TinyTableHeader
(Intercept)                                                  & \num{-0.05}      \\
& (\num{15.64})    \\
cd\_occupied                                                & \num{0.15}       \\
& (\num{10.22})    \\
district\_typeFrench Concession                             & \num{-0.11}      \\
& (\num{9.98})     \\
district\_typeInternational Settlement                      & \num{0.07}       \\
& (\num{9.83})     \\
french\_surrender                                           & \num{-0.06}      \\
& (\num{10.22})    \\
is\_occupied                                                & \num{-0.17}      \\
& (\num{9.95})     \\
cd\_occupied × district\_typeFrench Concession             & \num{-0.07}      \\
& (\num{9.95})     \\
cd\_occupied × district\_typeInternational Settlement      & \num{-0.06}      \\
& (\num{9.81})     \\
district\_typeFrench Concession × french\_surrender        & \num{0.01}       \\
& (\num{9.96})     \\
district\_typeInternational Settlement × french\_surrender & \num{-0.02}      \\
& (\num{10.01})    \\
district\_typeFrench Concession × is\_occupied             & \num{0.01}       \\
& (\num{10.20})    \\
district\_typeInternational Settlement × is\_occupied      & \num{0.00}       \\
& (\num{9.85})     \\
Num.Obs.                                                     & \num{21}         \\
R2                                                           & \num{0.000}      \\
Log.Lik.                                                     & \num{-325.376}   \\
RMSE                                                         & \num{1293540.34} \\
\bottomrule
\end{tblr}
\end{table}

@@

@@

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{tabularray}
\usepackage[normalem]{ulem}
\usepackage{graphicx}
\UseTblrLibrary{booktabs}
\UseTblrLibrary{siunitx}
\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}
\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={My title},
  pdfauthor={Sandy Yu},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{My title\thanks{Code and data are available at:
https://github.com/Jingying-yu/Shanghai\_population\_change}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Impact Analysis of Japanese Occupation on Population Shifts
Across Shanghai's Districts During WWII}
\author{Sandy Yu}
\date{December 1, 2024}

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable, sharp corners, interior hidden]}{\end{tcolorbox}}\fi

@@

\begin{itemize}
\tightlist
\item
  talk about where the data in my primary reference book is gathered
\item
  mentions the credibility of source and instability of recording
  instrument \& methodology
\end{itemize}

@@

Important Event Timeline

1. 1937-08-13: Japanese armed forces entered Shanghai

2. 1937-11-12: Japanese armed forces claims occupation of Shanghai
--\textgreater{} ends Chinese district

3. 1942-01: Japanese armed forces claims authority over International
Settlement (which was mainly under the governance of U.K and U.S prior
to this date)

4. 1945-08-15: Japan surrendered in WWII

5. 1945-10: most Japanese armed forces withdrew from Shanghai

\hypertarget{measurement-methodology}{%
\subsection{Measurement \& Methodology}\label{measurement-methodology}}

\begin{itemize}
\tightlist
\item
  how population is recorded
\item
  Why choose 1936 - 1942 (ex. if an event occurred in Nov of 1937, would
  I take values of 1937 as a variable for prior to event occurrence or
  after?)
\end{itemize}

Survey Difficulties - Population Volatility caused by Warfare:
Population is extreme volatile within this time period, population
shifts constantly as 战况 proceed - Regional Recording Limitations:
Survey response collect difficulty varies between districts. -
Resistance due to Political Risk

\hypertarget{variables-of-interest}{%
\subsection{Variables of Interest}\label{variables-of-interest}}

\hypertarget{tbl-outcome_variable}{}
\begin{longtable}[]{@{}cccc@{}}
\caption{\label{tbl-outcome_variable}Explanatory models of flight time
based on wing width and wing length}\tabularnewline
\toprule\noalign{}
Year & Pop CHN District & Pop IS & Pop FC \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Year & Pop CHN District & Pop IS & Pop FC \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
1936 & 2155717 & 1180969 & 477629 \\
1937 & 2155717 & 1218630 & 477629 \\
1938 & 2074693 & 1272552 & 504731 \\
1939 & 2098331 & 1257703 & 495942 \\
1940 & 1479726 & 1233394 & 477629 \\
1941 & 957339 & 446692 & 835523 \\
1942 & 1049403 & 1585673 & 854380 \\
\end{longtable}

\hypertarget{outcome-variable}{%
\subsubsection{Outcome variable}\label{outcome-variable}}

\begin{itemize}
\tightlist
\item
  outcome variable is \emph{population} with subscript of time (t) and
  district (i), where time range is between 1936-1942, and district is
  either: Chinese-administrated District, International Settlement, and
  French Concession. ``population change in International Settlement
  during 1937-1942'' measured in \# of persons
\end{itemize}

\hypertarget{predictor-variables}{%
\subsubsection{Predictor variables}\label{predictor-variables}}

\begin{itemize}
\tightlist
\item
  Event indicators (dummy variables)
\end{itemize}

\begin{table}

\end{table}

@@

Background details and diagnostics are included in Appendix
{[}Section~\ref{sec-model-details}{]}.

@@

\[y_i|\mu_i, \sigma \sim \text{Normal}(\mu_{i,t}, \sigma)\]

\[\alpha \sim \text{Normal}(0, 2.5)\]

\[\beta_k \sim \text{Normal}(0, 2.5) \quad \text{for } k = 1, ..., 11\]

\[\sigma \sim \text{Exponential}(1)\]

Where:

\begin{itemize}
\tightlist
\item
  \(y_i\): Observed population in district i at year t.
\item
  \(\text{cd_occupied}\): Indicator for whether the Chinese-administered
  district was occupied by Japanese forces in year t (1 if
  \(t \geq 1937\), 0 otherwise).
\item
  \(\text{french_surrender}\): Indicator for the French Surrendering to
  Germany in 1940, leading to the French Concession rejecting refugees
  in Shanghai (1 if \(t \geq 1940\), 0 otherwise).
\item
  \(\text{is_occupied}\): Indicator for the Japanese occupation of the
  International Settlement in 1942 (1 if \(t \geq 1942\), 0 otherwise).
\item
  \(\text{district_type}\): Dummy variable for International Settlement
  districts (1 if \(i\) is IS, 0 otherwise).
\item
  \(\text{district_type}\): Dummy variable for French Concession
  districts (1 if \(i\) is FC, 0 otherwise).
\end{itemize}

Interaction Terms:

The interaction terms in the model are essential because they capture
how the impact of historical events (e.g., the 1937 occupation of
Chinese-administered districts, the 1940 refugee rejection in the French
Concession, and the 1942 occupation of the International Settlement)
varies across different district types. By including interactions
between event indicators and district types, the model accounts for
district-specific responses to each event, controlling for the fact that
the effect of an event on population changes may not be uniform across
all districts. For instance, the 1937 occupation might lead to
population declines in Chinese-administered districts but population
increases in the International Settlement due to refugee influx. These
terms ensure that the model can differentiate and estimate the unique
effects of each event within each district type, thereby improving
precision and interpretability.

\begin{itemize}
\tightlist
\item
  \(\text{cd_occupied} \cdot \text{district_type}\): Captures the effect
  of the 1937 occupation on the International Settlement in comparison
  to the Chinese-administered district (base district).
\item
  \(\text{cd_occupied} \cdot \text{district_type}\): Captures the effect
  of the 1937 occupation on the French Concession in comparison to the
  base district.
\item
  \(\text{french_surrender} \cdot \text{district_type}\): Effect of the
  1940 refugee rejection on the International Settlement.
\item
  \(\text{french_surrender} \cdot \text{district_type}\): Effect of the
  1940 refugee rejection on the French Concession.
\item
  \(\text{is_occupied} \cdot \text{district_type}\): Effect of the 1942
  occupation on the International Settlement.
\item
  \(\text{is_occupied} \cdot \text{district_type}\): Effect of the 1942
  occupation on the French Concession.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  Data Trend Visualization
\end{itemize}

{\centering \includegraphics{paper_files/figure-pdf/fig-pop-1.pdf}

\caption{\label{fig-pop}Population in Shanghai between 1936 - 1942}

\begin{itemize}
\tightlist
\item
  Model results are summarized in Table~\ref{tbl-modelresults} in
  Appendix (Section~\ref{sec-model-details}).
\end{itemize}

\hypertarget{district-impact-on-population}{%
\paragraph{District Impact on
Population}\label{district-impact-on-population}}

\hypertarget{tbl-district}{}
\begin{longtable}[]{@{}ccc@{}}
\caption{\label{tbl-district}Explanatory models of flight time based on
wing width and wing length}\tabularnewline
\toprule\noalign{}
Parameters & Estimated Effect & Standard Error \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Parameters & Estimated Effect & Standard Error \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
(Intercept) & 117928165.6 & 189545438.8 \\
district\_is & -943281.6 & 381299.4 \\
district\_fc & -1642126.9 & 350808.4 \\
\end{longtable}

\hypertarget{historical-events}{%
\paragraph{Historical Events}\label{historical-events}}

\hypertarget{tbl-events}{}
\begin{longtable}[]{@{}ccc@{}}
\caption{\label{tbl-events}Explanatory models of flight time based on
wing width and wing length}\tabularnewline
\toprule\noalign{}
Parameters & Estimated Effect & Standard Error \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Parameters & Estimated Effect & Standard Error \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
cd\_occupied & 89350.01 & 350665.6 \\
french\_surrender & -735223.28 & 340852.1 \\
is\_occupied & -88982.32 & 361506.9 \\
\end{longtable}

\hypertarget{historic-events-impact-on-each-district}{%
\paragraph{Historic Events' Impact on Each
District}\label{historic-events-impact-on-each-district}}

\begin{verbatim}
# A tibble: 6 x 3
  term                         estimate std.error
  <chr>                           <dbl>     <dbl>
1 is_occupied                   -88982.   361507.
2 district_is:cd_occupied        89431.   414727.
3 district_fc:cd_occupied        38397.   410271.
4 district_is:french_surrender  470618.   352216.
5 district_fc:french_surrender 1044471.   352470.
6 district_is:is_occupied       934059.   476934.
\end{verbatim}

\hypertarget{tbl-events_district}{}
\begin{longtable}[]{@{}ccc@{}}
\caption{\label{tbl-events_district}Explanatory models of flight time
based on wing width and wing length}\tabularnewline
\toprule\noalign{}
Parameters & Estimated Effect & Standard Error \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Parameters & Estimated Effect & Standard Error \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
is\_occupied & -88982.32 & 361506.9 \\
district\_is:cd\_occupied & 89430.69 & 414726.8 \\
district\_fc:cd\_occupied & 38396.87 & 410271.2 \\
district\_is:french\_surrender & 470617.65 & 352215.9 \\
district\_fc:french\_surrender & 1044470.54 & 352469.9 \\
district\_is:is\_occupied & 934059.10 & 476934.2 \\
\end{longtable}

@@

\hypertarget{interpretation-of-the-event-impacts}{%
\subsection{Interpretation of the Event
Impacts}\label{interpretation-of-the-event-impacts}}

@@

\hypertarget{model-summary-table}{%
\subsection{Model Summary Table}\label{model-summary-table}}

\centering
\begin{tblr}[         %% tabularray outer open
]                     %% tabularray outer close
{                     %% tabularray inner open
colspec={Q[]Q[]},
column{1}={halign=l,},
column{2}={halign=c,},
hline{28}={1,2}{solid, 0.05em, black},
}                     %% tabularray inner close
\toprule
& Population model \\ \midrule %% TinyTableHeader
(Intercept)                        & \num{117928165.58}   \\
& (\num{189545438.85}) \\
year                               & \num{-59841.02}      \\
& (\num{98298.59})     \\
district\_is                      & \num{-943281.63}     \\
& (\num{381299.41})    \\
district\_fc                      & \num{-1642126.91}    \\
& (\num{350808.44})    \\
cd\_occupied                      & \num{89350.01}       \\
& (\num{350665.57})    \\
french\_surrender                 & \num{-735223.28}     \\
& (\num{340852.10})    \\
is\_occupied                      & \num{-88982.32}      \\
& (\num{361506.88})    \\
district\_is × cd\_occupied      & \num{89430.69}       \\
& (\num{414726.84})    \\
district\_fc × cd\_occupied      & \num{38396.87}       \\
& (\num{410271.18})    \\
district\_is × french\_surrender & \num{470617.65}      \\
& (\num{352215.89})    \\
district\_fc × french\_surrender & \num{1044470.54}     \\
& (\num{352469.86})    \\
district\_is × is\_occupied      & \num{934059.10}      \\
& (\num{476934.16})    \\
district\_fc × is\_occupied      & \num{377436.02}      \\
& (\num{466616.20})    \\
Num.Obs.                           & \num{21}             \\
R2                                 & \num{0.837}          \\
Log.Lik.                           & \num{-289.106}       \\
RMSE                               & \num{162825.22}      \\
\bottomrule
\end{tblr}
\end{table}
